Figures

### 2019-07-12 figures/06_lulc_buffer_demo.Rmd
rename panel title

cowplot::plot_grid(
  g_nlcd_agg + ggtitle("Total Ag"), 
  g_nlcd + ggtitle("Row Crops"), 
  g_cdl + ggtitle("Individual Crops"), 
                   rel_widths = c(0.95, 1, 0.95), nrow = 1)
```

>>>>

cowplot::plot_grid(
  g_nlcd_agg + ggtitle("Total Ag"), 
  g_nlcd + ggtitle("Ag Cover Type"), 
  g_cdl + ggtitle("Individual Crops"), 
                   rel_widths = c(0.95, 1, 0.95), nrow = 1)
```
